# Temporal change - mutualists

## Dependencies and setup

```{r}
library(tidyverse)
library(cowplot)
library(RColorBrewer)
library(khroma)
library(rstatix)
library(knitr)
library(kableExtra)
library(viridis)
```

```{r}
# Build relative path from R's working directory to what is actually the working
# directory for this experiment.
experiment_slug <- "2026-09-17-temporal-change-mutualists"
working_directory <- paste(
  "experiments",
  experiment_slug,
  "analysis",
  sep = "/"
)
```

```{r}
# Use the cowplot theme as our default for ggplots
theme_set(theme_cowplot())
# Create directory to save plots
plot_dir <- paste(
  working_directory,
  "plots",
  sep = "/"
)
dir.create(
  plot_dir,
  showWarnings = FALSE
)
```

### Load and preprocess data

```{r}
tasks <- c("NOT", "NAND", "OR_NOT", "AND", "OR", "AND_NOT", "NOR", "XOR", "EQU")
max_pop_size <- 100 * 100
threshold <- 0.025 * max_pop_size
```

Load summary data.

```{r}
summary_data_path <- paste(
  working_directory,
  "data",
  "summary.csv",
  sep = "/"
)
summary_data <- read_csv(summary_data_path)
# Do any universal preprocessing
summary_data <- summary_data %>%
  mutate(
    SEED = as.factor(SEED),
    START_MOI = as.factor(START_MOI),
    VERTICAL_TRANSMISSION = as.factor(VERTICAL_TRANSMISSION),
    HEALTH_TYPE = as.factor(HEALTH_TYPE),
    HEALTH_INTERACTION_CHANCE = as.factor(HEALTH_INTERACTION_CHANCE),
    MUTUALIST_CYCLE_GAIN_PROP = as.factor(MUTUALIST_CYCLE_GAIN_PROP),
    PARASITE_CYCLE_LOSS_PROP = as.factor(PARASITE_CYCLE_LOSS_PROP),
    PARASITE_BASE_CYCLE_PROP = as.factor(PARASITE_BASE_CYCLE_PROP),
    MUTUALIST_CYCLE_DONATE_MULTIPLIER = as.factor(MUTUALIST_CYCLE_DONATE_MULTIPLIER), # nolint: line_length_linter.
    PARASITE_CYCLE_STEAL_MULTIPLIER = as.factor(PARASITE_CYCLE_STEAL_MULTIPLIER), # nolint: line_length_linter.
    HOST_ONLY_FIRST_TASK_CREDIT = as.factor(HOST_ONLY_FIRST_TASK_CREDIT),
    SYM_ONLY_FIRST_TASK_CREDIT = as.factor(SYM_ONLY_FIRST_TASK_CREDIT),
    EVENTS_CFG_PATH = as.factor(EVENTS_CFG_PATH)
  ) %>%
  mutate(
    task_credit = paste0(
      "H", HOST_ONLY_FIRST_TASK_CREDIT,
      "S", SYM_ONLY_FIRST_TASK_CREDIT
    ),
    sym_condition = case_when(
      START_MOI == "0" ~ "no-syms",
      START_MOI == "1" & HEALTH_TYPE == "parasite" ~ "parasite",
      START_MOI == "1" & HEALTH_TYPE == "mutualist" ~ "mutualist",
      .default = "unknown" # precaution against unexpected parameterizations
    ),
    interaction_multiplier = as.factor(PARASITE_CYCLE_STEAL_MULTIPLIER),
    environment = case_when(
      EVENTS_CFG_PATH == "events-constant.json" ~ "constant",
      EVENTS_CFG_PATH == "events-fluctuating-25.json" ~ "fluct-25",
      EVENTS_CFG_PATH == "events-fluctuating-50.json" ~ "fluct-50",
      EVENTS_CFG_PATH == "events-fluctuating-100.json" ~ "fluct-100",
      EVENTS_CFG_PATH == "events-fluctuating-200.json" ~ "fluct-200",
      .default = "unknown"
    )
  ) %>%
  mutate(
    environment = factor(
      environment,
      levels = c(
        "fluct-25",
        "fluct-50",
        "fluct-100",
        "fluct-200",
        "constant"
      )
    ),
    treatment = paste0(
      sym_condition, "_", environment
    )
  ) %>%
  mutate(
    treatment = as.factor(
      treatment
    )
  )
```

Load time series data.

```{r}
time_data_path <- paste(
  working_directory,
  "data",
  "time_series.csv",
  sep = "/"
)
time_data <- read_csv(time_data_path)

# Do any universal preprocessing
time_data <- time_data %>%
  mutate(
    SEED = as.factor(SEED),
    START_MOI = as.factor(START_MOI),
    HEALTH_TYPE = as.factor(HEALTH_TYPE),
    EVENTS_CFG_PATH = as.factor(EVENTS_CFG_PATH)
  ) %>%
  mutate(
    sym_condition = case_when(
      START_MOI == "0" ~ "no-syms",
      START_MOI == "1" & HEALTH_TYPE == "parasite" ~ "parasite",
      START_MOI == "1" & HEALTH_TYPE == "mutualist" ~ "mutualist",
      .default = "unknown" # precaution against unexpected parameterizations
    ),
    environment = case_when(
      EVENTS_CFG_PATH == "events-constant.json" ~ "constant",
      EVENTS_CFG_PATH == "events-fluctuating-25.json" ~ "fluct-25",
      EVENTS_CFG_PATH == "events-fluctuating-50.json" ~ "fluct-50",
      EVENTS_CFG_PATH == "events-fluctuating-100.json" ~ "fluct-100",
      EVENTS_CFG_PATH == "events-fluctuating-200.json" ~ "fluct-200",
      .default = "unknown"
    )
  ) %>%
  mutate(
    environment = factor(
      environment,
      levels = c(
        "fluct-25",
        "fluct-50",
        "fluct-100",
        "fluct-200",
        "constant"
      )
    ),
    treatment = paste0(
      sym_condition, "_", environment
    )
  ) %>%
  mutate(
    treatment = as.factor(
      treatment
    )
  )
```


## Which runs had hosts and/or symbiont populations that went extinct?

```{r}
sym_min_pop_sizes <- time_data %>%
  group_by(SEED) %>%
  slice_min(
    OrgCounts_hosted_sym_count,
    n = 1
  ) %>%
  slice_min(
    update,
    n = 1
  )

reps_with_extinct_syms <- sym_min_pop_sizes %>%
  group_by(
    treatment
  ) %>%
  summarize(
    reps_with_extinct_syms = sum(OrgCounts_hosted_sym_count == 0)
  )

host_min_pop_sizes <- time_data %>%
  group_by(SEED) %>%
  slice_min(
    OrgCounts_host_count,
    n = 1
  ) %>%
  slice_min(
    update,
    n = 1
  )

reps_with_extinct_hosts <- host_min_pop_sizes %>%
  group_by(
    treatment
  ) %>%
  summarize(
    reps_with_extinct_hosts = sum(OrgCounts_host_count == 0)
  )

extinctions <- full_join(
  reps_with_extinct_syms,
  reps_with_extinct_hosts
)
extinctions <- extinctions %>%
  arrange(
    desc(reps_with_extinct_hosts), desc(reps_with_extinct_syms)
  )
extinction_table <- kable(extinctions) %>%
  kable_styling(latex_options = "striped")
save_kable(
  extinction_table,
  paste(
    plot_dir,
    "extinctions.pdf",
    sep = "/"
  )
)
```

## Task performance all time

### Hosts

Quantify whether tasks have been performed over course of entire run.

```{r}
# Pivot task data long:
# 1) Select only relevant columns
host_over_time_parent_task_data <- time_data %>%
  select(
    SEED,
    treatment,
    sym_condition,
    environment,
    update,
    CurUpdate_AND_NOT_in_host_parent_org_counts,
    CurUpdate_AND_in_host_parent_org_counts,
    CurUpdate_EQU_in_host_parent_org_counts,
    CurUpdate_NAND_in_host_parent_org_counts,
    CurUpdate_NOR_in_host_parent_org_counts,
    CurUpdate_NOT_in_host_parent_org_counts,
    CurUpdate_OR_NOT_in_host_parent_org_counts,
    CurUpdate_OR_in_host_parent_org_counts,
    CurUpdate_XOR_in_host_parent_org_counts
  ) %>%
  pivot_longer(
    c(
      CurUpdate_AND_NOT_in_host_parent_org_counts,
      CurUpdate_AND_in_host_parent_org_counts,
      CurUpdate_EQU_in_host_parent_org_counts,
      CurUpdate_NAND_in_host_parent_org_counts,
      CurUpdate_NOR_in_host_parent_org_counts,
      CurUpdate_NOT_in_host_parent_org_counts,
      CurUpdate_OR_NOT_in_host_parent_org_counts,
      CurUpdate_OR_in_host_parent_org_counts,
      CurUpdate_XOR_in_host_parent_org_counts
    ),
    names_to = "task",
    values_to = "task_in_parent_count"
  ) %>%
  mutate(
    task = str_replace(task, "CurUpdate_", "")
  ) %>%
  mutate(
    task = str_replace(task, "_in_host_parent_org_counts", "")
  ) %>%
  mutate(
    task_completed_by_parent = task_in_parent_count >= threshold,
    task = factor(
      task,
      levels = tasks,
      labels = tasks
    )
  ) %>%
  mutate(
    task_complexity = case_when(
      task == "NOT" ~ 1,
      task == "NAND" ~ 1,
      task == "OR_NOT" ~ 2,
      task == "AND" ~ 2,
      task == "OR" ~ 3,
      task == "AND_NOT" ~ 3,
      task == "NOR" ~ 4,
      task == "XOR" ~ 4,
      task == "EQU" ~ 5,
      .default = -1
    )
  )

host_parent_tasks_all_time_by_task <- host_over_time_parent_task_data %>%
  # filter(update <= 100000) %>%
  group_by(
    SEED,
    treatment,
    sym_condition,
    environment,
    task
  ) %>%
  summarize(
    n = n(),
    parent_task_completed_ever = any(task_completed_by_parent)
  ) %>%
  ungroup() %>%
  group_by(
    treatment,
    sym_condition,
    environment,
    task
  ) %>%
  summarize(
    n = n(),
    parent_tasks_completed_ever = sum(parent_task_completed_ever == TRUE)
  )
```

Additionally, summarize by task complexity level.

```{r}
host_max_task_complexity_data <- host_over_time_parent_task_data %>%
  group_by(
    SEED,
    treatment,
    sym_condition,
    environment,
    task,
    task_complexity
  ) %>%
  summarize(
    n = n(),
    parent_task_completed_ever = any(task_completed_by_parent)
  ) %>%
  ungroup() %>%
  # This filter works fine because all replicates start with a task
  filter(
    parent_task_completed_ever
  ) %>%
  group_by(
    SEED,
    treatment,
    sym_condition,
    environment
  ) %>%
  summarize(
    max_task_complexity = max(task_complexity)
  ) %>%
  mutate(
    sym_condition = factor(
      sym_condition,
      levels = c(
        "no-syms",
        "parasite",
        "mutualist"
      )
    )
  )
```

```{r}
host_parent_tasks_all_time_by_task <- host_parent_tasks_all_time_by_task %>%
  mutate(
    sym_condition = factor(
      sym_condition,
      levels = c(
        "no-syms",
        "parasite",
        "mutualist"
      )
    )
  )
host_parent_tasks_all_time_by_task_plt <- host_parent_tasks_all_time_by_task %>%
  ggplot(
    aes(
      x = task,
      color = sym_condition,
      fill = sym_condition,
      y = parent_tasks_completed_ever
    )
  ) +
  geom_col(
    position = "dodge",
    alpha = 0.5
  ) +
  geom_text(
    aes(label = parent_tasks_completed_ever),
    position = position_dodge(width = 1),
    vjust = -0.5,
    size = 2
  ) +
  scale_color_bright() +
  scale_fill_bright() +
  scale_x_discrete() +
  scale_y_continuous(
    limits = c(0, 11)
  ) +
  facet_wrap(
    ~environment,
    nrow = 1,
    axes = "all_x",
    labeller = label_both
  ) +
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(
      angle = 90,
      hjust = 1
    )
  )
ggsave(
  file = paste(plot_dir, "host_parent_tasks_all_time_by_task_plt.pdf", sep = "/"),
  plot = host_parent_tasks_all_time_by_task_plt,
  width = 15,
  height = 8
)
```

Total different tasks (all time)

```{r}
host_total_different_parent_tasks_all_time <- host_over_time_parent_task_data %>%
  group_by(
    SEED,
    treatment,
    sym_condition,
    environment,
    task
  ) %>%
  # Summarize across updates whether task was ever completed by a parent.
  summarize(
    n = n(),
    parent_task_completed_ever = any(task_completed_by_parent)
  ) %>%
  ungroup() %>%
  group_by(
    SEED,
    treatment,
    sym_condition,
    environment,
  ) %>%
  # Summarize across tasks (by seed)
  summarize(
    n = n(),
    num_parent_tasks_completed_ever = sum(parent_task_completed_ever == TRUE)
  )
```

Average number of different tasks evolved?

```{r}
host_avg_tasks_table <- host_total_different_parent_tasks_all_time %>%
  group_by(treatment) %>%
  summarize(
    avg_diff_num_host_parent_tasks = mean(num_parent_tasks_completed_ever)
  ) %>%
  arrange(desc(avg_diff_num_host_parent_tasks)) %>%
  kable() %>%
  kable_styling(latex_options = "striped")
save_kable(
  host_avg_tasks_table,
  paste(
    plot_dir,
    "host_avg_diff_num_host_parent_tasks.pdf",
    sep = "/"
  )
)
```

Maximum task complexity evolved

```{r}
host_max_task_complexity_plt <- host_max_task_complexity_data %>%
  ggplot(
    aes(
      x = sym_condition,
      fill = sym_condition,
      y = max_task_complexity
    )
  ) +
  geom_point(
    mapping = aes(color = sym_condition),
    position = position_jitterdodge(
      jitter.width = 0.15,
      jitter.height = 0.1
    ),
    size = .5,
    alpha = 0.8
  ) +
  geom_boxplot(
    width = .1,
    outlier.shape = NA,
    alpha = 0.5,
    position = position_dodge()
  ) +
  scale_x_discrete() +
  facet_wrap(~environment, nrow=1) +
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(
      angle = 60,
      hjust = 1
    )
  )
ggsave(
  file = paste(plot_dir, "host_max_task_complexity_plt.pdf", sep = "/"),
  plot = host_max_task_complexity_plt,
  width = 10,
  height = 10
)
```

### Symbionts

Quantify whether tasks have been performed over course of entire run.

```{r}
# Pivot task data long:
# 1) Select only relevant columns
over_time_sym_parent_task_data <- time_data %>%
  select(
    SEED,
    treatment,
    sym_condition,
    environment,
    update,
    CurUpdate_AND_NOT_in_sym_parent_org_counts,
    CurUpdate_AND_in_sym_parent_org_counts,
    CurUpdate_EQU_in_sym_parent_org_counts,
    CurUpdate_NAND_in_sym_parent_org_counts,
    CurUpdate_NOR_in_sym_parent_org_counts,
    CurUpdate_NOT_in_sym_parent_org_counts,
    CurUpdate_OR_NOT_in_sym_parent_org_counts,
    CurUpdate_OR_in_sym_parent_org_counts,
    CurUpdate_XOR_in_sym_parent_org_counts
  ) %>%
  pivot_longer(
    c(
      CurUpdate_AND_NOT_in_sym_parent_org_counts,
      CurUpdate_AND_in_sym_parent_org_counts,
      CurUpdate_EQU_in_sym_parent_org_counts,
      CurUpdate_NAND_in_sym_parent_org_counts,
      CurUpdate_NOR_in_sym_parent_org_counts,
      CurUpdate_NOT_in_sym_parent_org_counts,
      CurUpdate_OR_NOT_in_sym_parent_org_counts,
      CurUpdate_OR_in_sym_parent_org_counts,
      CurUpdate_XOR_in_sym_parent_org_counts
    ),
    names_to = "task",
    values_to = "task_in_parent_count"
  ) %>%
  mutate(
    task = str_replace(task, "CurUpdate_", "")
  ) %>%
  mutate(
    task = str_replace(task, "_in_sym_parent_org_counts", "")
  ) %>%
  mutate(
    task_completed_by_parent = task_in_parent_count >= threshold,
    task = factor(
      task,
      levels = tasks,
      labels = tasks
    )
  )

sym_parent_tasks_all_time_by_task <- over_time_sym_parent_task_data %>%
  group_by(
    SEED,
    treatment,
    sym_condition,
    environment,
    task
  ) %>%
  summarize(
    n = n(),
    parent_task_completed_ever = any(task_completed_by_parent)
  ) %>%
  ungroup() %>%
  group_by(
    treatment,
    sym_condition,
    environment,
    task
  ) %>%
  summarize(
    n = n(),
    parent_tasks_completed_ever = sum(parent_task_completed_ever == TRUE)
  )

# parent_tasks_all_time_total <- parent_tasks_all_time_by_task %>%

```

```{r}
sym_parent_tasks_all_time_by_task <- sym_parent_tasks_all_time_by_task %>%
  mutate(
    sym_condition = factor(
      sym_condition,
      levels = c(
        "no-syms",
        "parasite",
        "mutualist"
      )
    )
  )
sym_parent_tasks_all_time_by_task_plt <- sym_parent_tasks_all_time_by_task %>%
  filter(sym_condition != "no-syms") %>%
  ggplot(
    aes(
      x = task,
      y = parent_tasks_completed_ever
    )
  ) +
  geom_col(
    position = "dodge",
    alpha = 0.5
  ) +
  geom_text(
    aes(label = parent_tasks_completed_ever),
    position = position_dodge(width = 1),
    vjust = -0.5,
    size = 2
  ) +
  scale_x_discrete() +
  scale_y_continuous(
    limits = c(0, 11)
  ) +
  facet_wrap(
    ~environment,
    nrow = 1,
    labeller = label_both
  ) +
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(
      angle = 90,
      hjust = 1
    )
  )
ggsave(
  file = paste(plot_dir, "sym_parent_tasks_all_time_by_task_plt.pdf", sep = "/"),
  plot = sym_parent_tasks_all_time_by_task_plt,
  width = 15,
  height = 8
)
```

## Phenotypic diversity

### Host diversity

#### Host number of task sets

Over time:

```{r}
host_parent_num_task_sets_plt <- time_data %>%
  filter(update %% 10000 == 0) %>%
  ggplot(
    aes(
      x = update,
      y = CurUpdate_host_parent_num_task_sets,
      color = sym_condition,
      fill = sym_condition
    )
  ) +
  stat_summary(fun = "mean", geom = "line") +
  stat_summary(
    fun.data = "mean_cl_boot",
    fun.args = list(conf.int = 0.95),
    geom = "ribbon",
    alpha = 0.2,
    linetype = 0
  ) +
  scale_color_bright() +
  scale_fill_bright() +
  facet_wrap(
    ~environment,
    ncol = 1,
    axes = "all_x",
    labeller = label_both
  ) +
  theme(
    legend.position = "bottom"
  )
ggsave(
  file = paste(plot_dir, "host_parent_num_task_sets_plt.pdf", sep = "/"),
  plot = host_parent_num_task_sets_plt,
  width = 8,
  height = 15
)
```

```{r}
host_parent_num_task_sets_fluct_together_plt <- time_data %>%
  filter(sym_condition != "no-syms") %>%
  ggplot(
    aes(
      x = update,
      y = CurUpdate_host_parent_num_task_sets,
      color = environment,
      fill = environment
    )
  ) +
  stat_summary(fun = "mean", geom = "line") +
  stat_summary(
    fun.data = "mean_cl_boot",
    fun.args = list(conf.int = 0.95),
    geom = "ribbon",
    alpha = 0.2,
    linetype = 0
  ) +
  scale_color_bright() +
  scale_fill_bright() +
  theme(
    legend.position = "bottom"
  )
ggsave(
  file = paste(plot_dir, "host_parent_num_task_sets_fluct_together_plt.pdf", sep = "/"),
  plot = host_parent_num_task_sets_fluct_together_plt,
  width = 15,
  height = 8
)
```

Final

```{r}
host_final_num_task_sets_elapsed_plt <- summary_data %>%
  ggplot(
    aes(
      x = sym_condition,
      fill = sym_condition,
      y = CurUpdate_host_parent_num_task_sets
    )
  ) +
  geom_point(
    mapping=aes(color = sym_condition),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8
  ) +
  geom_boxplot(
    width = .1,
    outlier.shape = NA,
    alpha = 0.5
  ) +
  scale_x_discrete() +
  facet_wrap(
    ~environment,
    nrow = 1
  ) +
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(
      angle = 60,
      hjust = 1
    )
  )
ggsave(
  file = paste(plot_dir, "host_final_num_task_sets_elapsed_plt.pdf", sep = "/"),
  plot = host_final_num_task_sets_elapsed_plt,
  width = 10,
  height = 10
)
```

#### Host entropy of task sets

```{r}
host_parent_entropy_task_sets_plt <- time_data %>%
  filter(update %% 10000 == 0) %>%
  ggplot(
    aes(
      x = update,
      y = CurUpdate_host_parent_entropy_task_sets,
      color = sym_condition,
      fill = sym_condition
    )
  ) +
  stat_summary(fun = "mean", geom = "line") +
  stat_summary(
    fun.data = "mean_cl_boot",
    fun.args = list(conf.int = 0.95),
    geom = "ribbon",
    alpha = 0.2,
    linetype = 0
  ) +
  scale_color_bright() +
  scale_fill_bright() +
  facet_wrap(
    ~environment,
    ncol = 1,
    axes = "all_x",
    labeller = label_both
  ) +
  theme(
    legend.position = "bottom"
  )
ggsave(
  file = paste(plot_dir, "host_parent_entropy_task_sets_plt.pdf", sep = "/"),
  plot = host_parent_entropy_task_sets_plt,
  width = 8,
  height = 15
)
```

```{r}
host_parent_entropy_task_sets_fluct_together_plt <- time_data %>%
  filter(update %% 10000 == 0) %>%
  ggplot(
    aes(
      x = update,
      y = CurUpdate_host_parent_entropy_task_sets,
      color = environment,
      fill = environment
    )
  ) +
  stat_summary(fun = "mean", geom = "line") +
  stat_summary(
    fun.data = "mean_cl_boot",
    fun.args = list(conf.int = 0.95),
    geom = "ribbon",
    alpha = 0.2,
    linetype = 0
  ) +
  scale_color_bright() +
  scale_fill_bright() +
  theme(
    legend.position = "bottom"
  )
ggsave(
  file = paste(plot_dir, "host_parent_entropy_task_sets_fluct_together_plt.pdf", sep = "/"),
  plot = host_parent_entropy_task_sets_fluct_together_plt,
  width = 15,
  height = 8
)
```


```{r}
host_final_entopy_task_sets_elapsed_plt <- summary_data %>%
  ggplot(
    aes(
      x = sym_condition,
      fill = sym_condition,
      y = CurUpdate_host_parent_entropy_task_sets
    )
  ) +
  geom_point(
    mapping=aes(color = sym_condition),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8
  ) +
  geom_boxplot(
    width = .1,
    outlier.shape = NA,
    alpha = 0.5
  ) +
  scale_x_discrete() +
  facet_wrap(
    ~environment,
    nrow = 1
  ) +
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(
      angle = 60,
      hjust = 1
    )
  )
ggsave(
  file = paste(plot_dir, "host_final_entopy_task_sets_elapsed_plt.pdf", sep = "/"),
  plot = host_final_entopy_task_sets_elapsed_plt,
  width = 10,
  height = 8
)
```

### Symbiont diversity

#### Symbiont number of task sets

```{r}
symbiont_parent_num_task_sets_plt <- time_data %>%
  filter(update %% 1000 == 0 & sym_condition != "no-syms") %>%
  ggplot(
    aes(
      x = update,
      y = CurUpdate_sym_parent_num_task_sets,
      color = environment,
      fill = environment
    )
  ) +
  stat_summary(fun = "mean", geom = "line") +
  stat_summary(
    fun.data = "mean_cl_boot",
    fun.args = list(conf.int = 0.95),
    geom = "ribbon",
    alpha = 0.2,
    linetype = 0
  ) +
  scale_color_bright() +
  scale_fill_bright() +
  theme(
    legend.position = "bottom"
  )
ggsave(
  file = paste(plot_dir, "symbiont_parent_num_task_sets_plt.pdf", sep = "/"),
  plot = symbiont_parent_num_task_sets_plt,
  width = 15,
  height = 8
)
```

#### Symbiont entropy of task sets

```{r}
symbiont_parent_entropy_task_sets_plt <- time_data %>%
  filter(update %% 1000 == 0 & sym_condition != "no-syms") %>%
  ggplot(
    aes(
      x = update,
      y = CurUpdate_sym_parent_entropy_task_sets,
      color = environment,
      fill = environment
    )
  ) +
  stat_summary(fun = "mean", geom = "line") +
  stat_summary(
    fun.data = "mean_cl_boot",
    fun.args = list(conf.int = 0.95),
    geom = "ribbon",
    alpha = 0.2,
    linetype = 0
  ) +
  scale_color_bright() +
  scale_fill_bright() +
  theme(
    legend.position = "bottom"
  )
ggsave(
  file = paste(plot_dir, "symbiont_parent_entropy_task_sets_plt.pdf", sep = "/"),
  plot = symbiont_parent_entropy_task_sets_plt,
  width = 15,
  height = 8
)
```

## Task profile matches over time

### Host-symbiont pair any matches count

```{r}
host_sym_any_matches_total_plt <- time_data %>%
  filter(update %% 500 == 0 & sym_condition != "no-syms") %>%
  ggplot(
    aes(
      x = update,
      y = CurUpdate_host_sym_any_matches_total,
      color = environment,
      fill = environment
    )
  ) +
  stat_summary(fun = "mean", geom = "line") +
  stat_summary(
    fun.data = "mean_cl_boot",
    fun.args = list(conf.int = 0.95),
    geom = "ribbon",
    alpha = 0.2,
    linetype = 0
  ) +
  scale_color_bright() +
  scale_fill_bright() +
  theme(
    legend.position = "bottom"
  )
ggsave(
  file = paste(plot_dir, "host_sym_any_matches_total_plt.pdf", sep = "/"),
  plot = host_sym_any_matches_total_plt,
  width = 15,
  height = 8
)
```

## Generations elapsed

### Hosts

```{r}
host_avg_gens_elapsed_plt <- summary_data %>%
  ggplot(
    aes(x = sym_condition, fill = sym_condition, y = CurUpdate_host_mean_generations)
  ) +
  geom_point(
    mapping = aes(color = sym_condition),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8
  ) +
  geom_boxplot(
    width = .1,
    outlier.shape = NA,
    alpha = 0.5
  ) +
  scale_x_discrete() +
  facet_wrap(
    ~environment,
    nrow = 1
  ) +
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(
      angle = 60,
      hjust = 1
    )
  )
ggsave(
  file = paste(plot_dir, "host_avg_gens_elapsed_plt.pdf", sep = "/"),
  plot = host_avg_gens_elapsed_plt,
  width = 15,
  height = 8
)
```

```{r}
summary_data %>%
  group_by(
    sym_condition,
    environment
  ) %>%
  summarise(
    mean_gens = mean(CurUpdate_host_mean_generations),
    median_gens = median(CurUpdate_host_mean_generations),
    var_gens = var(CurUpdate_host_mean_generations),
    sdev_gens = sd(CurUpdate_host_mean_generations)
  )
```

### Symbionts

```{r}
sym_avg_gens_elapsed_plt <- summary_data %>%
  filter(sym_condition != "no-syms") %>%
  ggplot(
    aes(x = environment, fill = environment, y = CurUpdate_sym_mean_generations)
  ) +
  geom_point(
    mapping = aes(color = environment),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8
  ) +
  geom_boxplot(
    width = .1,
    outlier.shape = NA,
    alpha = 0.5
  ) +
  scale_x_discrete() +
  theme(
    legend.position = "none",
    axis.text.x = element_text(
      angle = 60,
      hjust = 1
    )
  )
ggsave(
  file = paste(plot_dir, "sym_avg_gens_elapsed_plt.pdf", sep = "/"),
  plot = sym_avg_gens_elapsed_plt,
  width = 10,
  height = 8
)
```

```{r}
summary_data %>%
  filter(sym_condition != "no-syms") %>%
  group_by(
    sym_condition,
    environment
  ) %>%
  summarise(
    mean_gens = mean(CurUpdate_sym_mean_generations),
    median_gens = median(CurUpdate_sym_mean_generations),
    var_gens = var(CurUpdate_sym_mean_generations),
    sdev_gens = sd(CurUpdate_sym_mean_generations)
  )
```

## Population size

Average / median population size

```{r}
pop_size_summary <- time_data %>%
  group_by(
    SEED,
    treatment
  ) %>%
  summarize(
    host_pop_size_avg = mean(OrgCounts_host_count),
    host_pop_size_median = median(OrgCounts_host_count),
    host_pop_size_variance = var(OrgCounts_host_count),
    sym_pop_size_avg = mean(OrgCounts_hosted_sym_count),
    sym_pop_size_median = median(OrgCounts_hosted_sym_count),
    sym_pop_size_variance = var(OrgCounts_hosted_sym_count)
  )
```

```{r}
host_pop_size_avg_plt <- pop_size_summary %>%
  ggplot(
    aes(x = treatment, fill = treatment, y = host_pop_size_avg)
  ) +
  geom_point(
    mapping=aes(color = treatment),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8
  ) +
  geom_boxplot(
    width = .1,
    outlier.shape = NA,
    alpha = 0.5
  ) +
  scale_x_discrete() +
  # facet_wrap(STRESS_FREQUENCY~stress_death_chance, labeller = label_both) +
  theme(
    legend.position = "none",
    axis.text.x = element_text(
      angle = 60,
      hjust = 1
    )
  )
ggsave(
  file = paste(plot_dir, "host_pop_size_avg_plt.pdf", sep = "/"),
  plot = host_pop_size_avg_plt,
  width = 10,
  height = 10
)
```

## Individual tasks over time

## Task performance over time

```{r}
over_time_sym_parent_task_data <- over_time_sym_parent_task_data %>%
  mutate(org_type = "symbiont")

host_over_time_parent_task_data <- host_over_time_parent_task_data %>%
  mutate(org_type = "host")

over_time_parent_task_data <- full_join(
  over_time_sym_parent_task_data,
  host_over_time_parent_task_data
)
over_time_parent_task_data <- over_time_parent_task_data %>%
  mutate(
    org_type = as.factor(org_type)
  )
```

```{r}
treatments <- levels(over_time_parent_task_data$treatment)

for (trt in treatments) {
  print(trt)
  p <- over_time_parent_task_data %>%
    filter(treatment == trt) %>%
    ggplot(
      aes(
        x = update / 200000,
        y = task_in_parent_count,
        color = org_type,
        fill = org_type
      )
    ) +
    geom_line() +
    labs(
      title = trt
    ) +
    facet_grid(
      SEED ~ task,
      scales = "free_y",
      labeller = label_both
    )

  ggsave(
    file = paste(
      plot_dir,
      paste0("tasks_over_time_", trt, ".pdf"),
      sep = "/"
    ),
    plot = p,
    width = 20,
    height = 40
  )
}
```
